The \textit{Kepler} Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-12-06 paper/ms.tex
quarters observed

We selected all stars on-silicon in \kepler with $Kp<9$ that were targeted for fewer than $8$ quarters. The majority of these were not previously targeted at all, but sixteen stars were to some extent observed conventionally: HD~174020 was targeted in LC for Q2, 6, 10, and 14; HD~175841 for Q11-12, 14-16, with SC for Q3; HD~176582 for Q12-13; HD~178090 for Q1, 3, and 10; HD~180682 for Q0, 3, and 7; HD~181069 for Q1, 10, 13, 14, and 17; HD~181878 for Q14-17; HD~182694 for Q2; HD~183124 for even quarters; HD~185351 for Q1-3 and with SC for Q16; HD~186155 for only Q1; HD~187217 for Q14-17; HD~188252 for only Q13; HD~189013 with SC for Q3 as a $\gamma$~Dor; V380~Cyg for Q11 and with SC for Q7, 9, 10, 12-17; and V819~Cyg for Q14, 16 and 17. A number of these lay at the edge of a detector, with the result that in some cadences the centroid of the star did not lie on the chip; light curves from these targets were found to be of extremely low quality and all of these stars were discarded. After applying these criteria we obtained a list of 102 targets, which are listed in Table~\ref{all_stars} with their \kepler magnitude $Kp$, together with their spectral type from SIMBAD, \gaia~DR2 apparent~$G$ magnitudes and $Bp-Rp$ colours, \gaia~DR2 calibrated distances from \citet{gaiadists}, variability classification and availability of TRES spectroscopy. The \kepler spacecraft rotates between quarters, so that it cycles through four orientation `seasons' each rotated from the last by $90^{\circ}$. Some stars were not on silicon for all seasons: we have only one season of HD~179394; two for HD~187277, HD~226754, V554~Lyr, and BD+47~2891; and three for BD+43~3064. The addition of our sample to the conventionally-observed stars makes the \kepler survey magnitude-complete down to $Kp=9$ for all stars on-silicon.

@@

Because the smear data are collected along an entire CCD~column, there is the risk of contamination from other bright stars. This is especially true when doing asteroseismology of red giants, where the low-amplitude stochastically-excited oscillations can be washed out in a power spectrum by the coherent high amplitude variations of a classical pulsator, even if the background star is much fainter. We can assess the importance of this contamination by considering the differences between odd and even quarters: because the \kepler spacecraft rotates $90^{\circ}$ between successive quarters, any contaminant will lie in the same column as a smear target only every second quarter. We have therefore generated Lomb-Scargle periodograms \citep{lomb,scargle} of each light curve, after clipping for outliers. We consider only odd and even quarters separately, and also the full combined time series. In the great majority of cases they closely resemble one another, indicating that contamination is at worst a minor effect. In order to better quantify this, we computed the inner product of normalized periodograms of the odd and even quarters, each smoothed with a 3-element Gaussian kernel. If this overlap integral is 1, then the power spectra are identical; substantial departures from unity may be caused by real nonstationary or long-period stellar variation, noise, or gain or contamination differences between the seasons. We found that the distribution of overlaps (Figure~\ref{contamination2}) is strongly peaked around $\sim 0.91$, with a tail of 22 stars showing overlap $< 0.9$. We investigate these further, finding that in some of these cases  there was no obvious problem. For example, the classical pulsator HD~175841 showed amplitude changes of several pulsations but the overall distribution seemed very similar, from which we conclude that the variation is probably astrophysical.

In the case of HD~181878, a red giant, there is clear and significant contamination from a star with several low-frequency pulsations, as is seen in Figure~\ref{contamination}. Likewise HD~183383 shows two different stars, depending on the quarter: some parts are likely from an ellipsoidal variable with a period of 6.46 days, other parts are from an RR Lyrae pulsator. Between seasons, there is an extra hump of power near the red giant oscillations in HD~175740; extra low frequency power in HD~180658; one coherent peak in  HD~182694; high frequency contamination in HD~181597 possibly from an EB; and a very significant difference in amplitude between seasons for BD~+39~3882. In other cases visual inspection does not show severe contamination, but in all cases we recommend that users of these light curves carefully check for differences between odd and even quarters.

>>>>

We selected all stars on-silicon in \kepler with $Kp<9$ that were targeted for fewer than $8$ quarters. The majority of these were not previously targeted at all, but sixteen stars were to some extent observed conventionally: these are listed in Table~\ref{quarters}. A number of these lay at the edge of a detector, with the result that in some cadences the centroid of the star did not lie on the chip; light curves from these targets were found to be of extremely low quality and all of these stars were discarded. After applying these criteria we obtained a list of 102 targets, which are listed in Table~\ref{all_stars} with their \kepler magnitude $Kp$, together with their spectral type from SIMBAD, \gaia~DR2 apparent~$G$ magnitudes and $Bp-Rp$ colours, \gaia~DR2 calibrated distances from \citet{gaiadists}, variability classification and availability of TRES spectroscopy. The \kepler spacecraft rotates between quarters, so that it cycles through four orientation `seasons' each rotated from the last by $90^{\circ}$. Some stars were not on silicon for all seasons: we have only one season of HD~179394; two for HD~187277, HD~226754, V554~Lyr, and BD+47~2891; and three for BD+43~3064. The addition of our sample to the conventionally-observed stars makes the \kepler survey magnitude-complete down to $Kp=9$ for all stars on-silicon.

\input{quarters.tex}

@@

We can assess the importance of this contamination by considering differences between quarters. Because the Kepler spacecraft rotates $90^\circ$ between successive quarters, stars are observed on different CCD modules with the exception of stars on the central Module 13. Minor variations in the precise alignment of each CCD mean that the contribution from contaminating stars varies from quarter to quarter. Differences are clearer for Module 13, where contaminating stars will only be aligned along the same columns as a smear target every second quarter. We have therefore generated Lomb-Scargle periodograms \citep{lomb,scargle} of each light curve, after clipping for outliers. We consider only odd and even quarters separately, and also the full combined time series. In the great majority of cases they closely resemble one another, indicating that contamination is at worst a minor effect. In order to better quantify this, we computed the inner product of normalized periodograms of the odd and even quarters, each smoothed with a 3-element Gaussian kernel. If this overlap integral is 1, then the power spectra are identical; substantial departures from unity may be caused by real nonstationary or long-period stellar variation, noise, or gain or contamination differences between the seasons. We found that the distribution of overlaps (Figure~\ref{contamination2}) is strongly peaked around $\sim 0.91$, with a tail of 22 stars showing overlap $< 0.9$. We investigate these further, finding that in some of these cases  there was no obvious problem. For example, the classical pulsator HD~175841 showed amplitude changes of several pulsations but the overall distribution seemed very similar, from which we conclude that the variation is probably astrophysical.

In the case of HD~181878, a red giant, there is clear and significant contamination from a star with several low-frequency pulsations, as is seen in Figure~\ref{contamination}. Likewise the light curve for HD 183383, which variously falls on Modules 8, 12, 14 and 18, shows different behaviour for different quarters: some parts are likely from an ellipsoidal variable with a period of 6.46 days, while other quarters are contaminated by the star RR Lyrae. Between seasons, there is an extra hump of power near the red giant oscillations in HD~175740; extra low frequency power in HD~180658; one coherent peak in  HD~182694; high frequency contamination in HD~181597 possibly from an EB; and a very significant difference in amplitude between seasons for BD~+39~3882. In other cases visual inspection does not show severe contamination, but in all cases we recommend that users of these light curves carefully check for differences between quarters, as well as investigating the full frame images for potential contaminants.
